Modelling potential environmental impacts of science activity in Antarctica

### 2025-09-24 talk/index.qmd
and finally finally

## [Conclusions]{style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"} {background-image="beacon-valley.jpg" style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"}
### Terrain-differentiated data-fitted hiking functions are a novelty
### Potential wider application of radius-limited betweenness centrality?
### Manuscript in preparation

@@

::: {style="background-color:rgba(102,0,0,0.1);"}
<h2 style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);">For more</h2>
### On this project [dosull.github.io/antarctica](https://dosull.github.io/antarctica) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
### About ![](logo.png){style="vertical-align:middle;width:60px;text-align:center;"} Geospatial Stuff [dosull.github.io](https://dosull.github.io) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
:::

>>>>

## [Conclusions]{style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"} {background-image="beacon-valley.jpg" style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"}

::: {style="background-color:rgba(102,0,0,0.25);"}
### Terrain-differentiated data-fitted hiking functions are a novelty
### Potential wider application of radius-limited betweenness centrality?
### Manuscript in preparation
### Start a conversation with Antarctic scientists about planning
:::

@@

::: {style="background-color:rgba(102,0,0,0.2);"}
<h2 style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);">For more</h2>
### On this project [dosull.github.io/antarctica](https://dosull.github.io/antarctica) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
### On ![](logo.png){style="vertical-align:middle;width:60px;text-align:center;"} Geospatial Stuff [dosull.github.io](https://dosull.github.io) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
:::
